---
title: "Vulgar language on the web across World Englishes - Part 3: data cleaning"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: word_document
bibliography: bibliography.bib
link-citations: yes
---

This document shows an analysis that was performed with the aim of finding differences in swearing across geographically distinct varieties of English around the world based on the GloWbe corpus. 

install packages

```{r install, eval = F, message=F, warning=F}
# install packages
install.packages("tidyverse")
install.packages("quanteda")
install.packages("here")
install.packages("udpipe")
install.packages("future")
install.packages("furrr")
install.packages("stringi")
install.packages("parallel")
```

load packages and set options

```{r act, message=FALSE, warning=FALSE}
# load packages
library(data.table)
library(tidyverse)
library(quanteda)
library(here)
library(stringi)
#library(udpipe)
library(parallel)
library(spacyr)
# load language model
#m_eng   <- udpipe::udpipe_download_model(language = "english-ewt")
#m_eng <- udpipe_load_model(file = here::here("english-ewt-ud-2.5-191206.udpipe"))
```

# Testing

## udpipe

```{r eval = F}
# Time difference of 8.818679 secs for 50 texts, spaCy less than 1.5 seconds 
# hence: using spaCy
testtxt <- base::readRDS(here::here("data", "glowbe_au_clean.rda")) %>%
  dplyr::slice_head(n = 50) %>%
  dplyr::filter(cleantext != "")
start_time <- Sys.time()

testtxt %>%
  dplyr::mutate(postext = lapply(cleantext, function(x){
      x <- udpipe::udpipe_annotate(m_eng, x = x) %>%
        as.data.frame() %>%
        dplyr::group_by(doc_id) %>%
        dplyr::summarise(postext = paste(.$token, "/", .$xpos, collapse = " ", sep = "")) %>%  
        dplyr::pull(postext) 
      }) %>% unlist(recursive = TRUE, use.names = FALSE)) -> test_pos

head(test_pos)
end_time <- Sys.time()
end_time - start_time
```

# spacy


```{r eval = F}
# Time difference of 8.356269 secs
testtxt <- base::readRDS(here::here("data", "glowbe_au_clean.rda")) %>%
  dplyr::slice_head(n = 50) %>%
  dplyr::filter(cleantext != "")
start_time <- Sys.time()

testtxt %>%
  dplyr::mutate(postext = lapply(cleantext, function(x){
      x <- udpipe::udpipe_annotate(m_eng, x = x) %>%
        as.data.frame() %>%
        dplyr::group_by(doc_id) %>%
        dplyr::summarise(postext = paste(.$token, "/", .$xpos, collapse = " ", sep = "")) %>%  
        dplyr::pull(postext) 
      }) %>% unlist(recursive = TRUE, use.names = FALSE)) -> test_pos

head(test_pos)
end_time <- Sys.time()
end_time - start_time
```


# Processing


## Australia

 
```{r eval = F}
glowbe_au_pos <- base::readRDS(here::here("data", "glowbe_au_clean.rda")) %>%
  dplyr::filter(cleantext != "")

start_time <- Sys.time()

# Initialize spaCy with a specific language model (e.g., English)
spacy_initialize(model = "en_core_web_sm")

glowbe_au_pos %>%
  dplyr::mutate(postext = spacy_parse(cleantext) %>%
  as.data.frame()  %>%
  dplyr::mutate(doc_id = factor(doc_id)) %>%
        dplyr::group_by(doc_id) %>%
        dplyr::summarise(postext = paste(token, "/", pos, collapse = " ", sep = "")) %>%  
        dplyr::pull(postext)) -> glowbe_au_pos

base::saveRDS(glowbe_au_pos, file = here::here("data", "glowbe_au_pos.rda"))

# Clean up and release resources
spacy_finalize()

head(glowbe_au_pos)
rm(glowbe_au_pos)
end_time <- Sys.time()
end_time - start_time
```




## Bangladesh


```{r eval = F}
glowbe_bd_pos <- base::readRDS(here::here("data", "glowbe_bd_clean.rda")) %>%
  dplyr::filter(cleantext != "")

start_time <- Sys.time()

# Initialize spaCy with a specific language model
spacy_initialize(model = "en_core_web_sm")

glowbe_bd_pos %>%
  dplyr::mutate(postext = spacy_parse(cleantext) %>%
  as.data.frame()  %>%
  dplyr::mutate(doc_id = factor(doc_id)) %>%
        dplyr::group_by(doc_id) %>%
        dplyr::summarise(postext = paste(token, "/", pos, collapse = " ", sep = "")) %>%  
        dplyr::pull(postext)) -> glowbe_bd_pos

base::saveRDS(glowbe_bd_pos, file = here::here("data", "glowbe_bd_pos.rda"))

# Clean up and release resources
spacy_finalize()

head(glowbe_bd_pos)
rm(glowbe_bd_pos)
end_time <- Sys.time()
end_time - start_time
```

## Canada

```{r eval = T}
glowbe_ca_pos <- base::readRDS(here::here("data", "glowbe_ca_clean.rda")) %>%
  dplyr::filter(cleantext != "")

start_time <- Sys.time()

# Initialize spaCy with a specific language model
spacy_initialize(model = "en_core_web_sm")

glowbe_ca_pos %>%
  dplyr::mutate(postext = spacy_parse(cleantext) %>%
  as.data.frame()  %>%
  dplyr::mutate(doc_id = factor(doc_id)) %>%
        dplyr::group_by(doc_id) %>%
        dplyr::summarise(postext = paste(token, "/", pos, collapse = " ", sep = "")) %>%  
        dplyr::pull(postext)) -> glowbe_ca_pos

base::saveRDS(glowbe_ca_pos, file = here::here("data", "glowbe_ca_pos.rda"))

# Clean up and release resources
spacy_finalize()

head(glowbe_ca_pos)
rm(glowbe_ca_pos)
end_time <- Sys.time()
end_time - start_time
```

## Great Britain

```{r vgb, message=FALSE, warning=FALSE}
# extract start time
start_time <- Sys.time()
# batch 1
postxt("glowbe_gb_clean1.rda") -> glowbe_gb1_pos
base::saveRDS(glowbe_gb1_pos, file = here::here("data", "glowbe_gb1_pos.rda"))
rm(glowbe_gb1_pos)
# batch 2
postxt("glowbe_gb_clean2.rda") -> glowbe_gb2_pos
base::saveRDS(glowbe_gb2_pos, file = here::here("data", "glowbe_gb2_pos.rda"))
rm(glowbe_gb2_pos)
# batch 2
postxt("glowbe_gb_clean3.rda") -> glowbe_gb3_pos
base::saveRDS(glowbe_gb3_pos, file = here::here("data", "glowbe_gb3_pos.rda"))
rm(glowbe_gb3_pos)
# batch 2
postxt("glowbe_gb_clean4.rda") -> glowbe_gb4_pos
base::saveRDS(glowbe_gb4_pos, file = here::here("data", "glowbe_gb4_pos.rda"))
rm(glowbe_gb4_pos)
# batch 2
postxt("glowbe_gb_clean5.rda") -> glowbe_gb5_pos
base::saveRDS(glowbe_gb5_pos, file = here::here("data", "glowbe_gb5_pos.rda"))
rm(glowbe_gb5_pos)
# extract end time
end_time <- Sys.time()
end_time - start_time
```

## Ghana

```{r vgh, message=FALSE, warning=FALSE}
# apply function to files
start_time <- Sys.time()
postxt("glowbe_gh_clean.rda") -> glowbe_gh_pos
base::saveRDS(glowbe_gh_pos, file = here::here("data", "glowbe_gh_pos.rda"))
rm(glowbe_gh_pos)
end_time <- Sys.time()
end_time - start_time
```


## Hong Kong

```{r vhk, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_hk_clean.rda") -> glowbe_hk_pos
base::saveRDS(glowbe_hk_pos, file = here::here("data", "glowbe_hk_pos.rda"))
rm(glowbe_hk_pos)
end_time <- Sys.time()
end_time - start_time
```

## Ireland

```{r vie, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_ie_clean.rda") -> glowbe_ie_pos
base::saveRDS(glowbe_ie_pos, file = here::here("data", "glowbe_ie_pos.rda"))
rm(glowbe_ie_pos)
end_time <- Sys.time()
end_time - start_time
```

## India

```{r vin, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_in_clean.rda") -> glowbe_in_pos
base::saveRDS(glowbe_in_pos, file = here::here("data", "glowbe_in_pos.rda"))
rm(glowbe_in_pos)
end_time <- Sys.time()
end_time - start_time
```


## Jamaica

```{r vjm, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_jm_clean.rda") -> glowbe_jm_pos
base::saveRDS(glowbe_jm_pos, file = here::here("data", "glowbe_jm_pos.rda"))
rm(glowbe_jm_pos)
end_time <- Sys.time()
end_time - start_time
```

## Kenia

```{r vke, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_ke_clean.rda") -> glowbe_ke_pos
base::saveRDS(glowbe_ke_pos, file = here::here("data", "glowbe_ke_pos.rda"))
rm(glowbe_ke_pos)
end_time <- Sys.time()
end_time - start_time
```


## Malaysia

```{r vmy, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_my_clean.rda") -> glowbe_my_pos
base::saveRDS(glowbe_my_pos, file = here::here("data", "glowbe_my_pos.rda"))
rm(glowbe_my_pos)
end_time <- Sys.time()
end_time - start_time
```


## Nigeria

```{r vng, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_ng_clean.rda") -> glowbe_ng_pos
base::saveRDS(glowbe_ng_pos, file = here::here("data", "glowbe_ng_pos.rda"))
rm(glowbe_ng_pos)
end_time <- Sys.time()
end_time - start_time
```


## New Zealand

```{r vnz, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_nz_clean.rda") -> glowbe_nz_pos
base::saveRDS(glowbe_nz_pos, file = here::here("data", "glowbe_nz_pos.rda"))
rm(glowbe_nz_pos)
end_time <- Sys.time()
end_time - start_time
```

## Philippines

```{r vph, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_ph_clean.rda") -> glowbe_ph_pos
base::saveRDS(glowbe_ph_pos, file = here::here("data", "glowbe_ph_pos.rda"))
rm(glowbe_ph_pos)
end_time <- Sys.time()
end_time - start_time
```

## Pakistan

```{r vpk, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_pk_clean.rda") -> glowbe_pk_pos
base::saveRDS(glowbe_pk_pos, file = here::here("data", "glowbe_pk_pos.rda"))
rm(glowbe_pk_pos)
end_time <- Sys.time()
end_time - start_time
```

## Singapore

```{r vsg, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_sg_clean.rda") -> glowbe_sg_pos
base::saveRDS(glowbe_sg_pos, file = here::here("data", "glowbe_sg_pos.rda"))
rm(glowbe_sg_pos)
end_time <- Sys.time()
end_time - start_time
```

## South Africa

```{r vza, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_za_clean.rda") -> glowbe_za_pos
base::saveRDS(glowbe_za_pos, file = here::here("data", "glowbe_za_pos.rda"))
rm(glowbe_za_pos)
end_time <- Sys.time()
end_time - start_time
```

## Sri Lanka

```{r vlk, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_lk_clean.rda") -> glowbe_lk_pos
base::saveRDS(glowbe_lk_pos, file = here::here("data", "glowbe_lk_pos.rda"))
rm(glowbe_lk_pos)
end_time <- Sys.time()
end_time - start_time
```

## Tanzania

```{r vtz, message=FALSE, warning=FALSE}
start_time <- Sys.time()
postxt("glowbe_tz_clean.rda") -> glowbe_tz_pos
base::saveRDS(glowbe_tz_pos, file = here::here("data", "glowbe_tz_pos.rda"))
rm(glowbe_tz_pos)
end_time <- Sys.time()
end_time - start_time
```


## USA

```{r vus, message=FALSE, warning=FALSE}
start_time <- Sys.time()
# batch 1
postxt("glowbe_us_clean1.rda") -> glowbe_us1_pos
base::saveRDS(glowbe_us1_pos, file = here::here("data", "glowbe_us1_pos.rda"))
rm(glowbe_us1_pos)
# batch 2
postxt("glowbe_us_clean2.rda") -> glowbe_us2_pos
base::saveRDS(glowbe_us2_pos, file = here::here("data", "glowbe_us2_pos.rda"))
rm(glowbe_us2_pos)
# batch 3
postxt("glowbe_us_clean3.rda") -> glowbe_us3_pos
base::saveRDS(glowbe_us3_pos, file = here::here("data", "glowbe_us3_pos.rda"))
rm(glowbe_us3_pos)
# batch 4
postxt("glowbe_us_clean4.rda") -> glowbe_us4_pos
base::saveRDS(glowbe_us4_pos, file = here::here("data", "glowbe_us4_pos.rda"))
rm(glowbe_us4_pos)
# batch 5
postxt("glowbe_us_clean5.rda") -> glowbe_us5_pos
base::saveRDS(glowbe_us5_pos, file = here::here("data", "glowbe_us5_pos.rda"))
rm(glowbe_us5_pos)
# batch 6
postxt("glowbe_us_clean6.rda") -> glowbe_us6_pos
base::saveRDS(glowbe_us6_pos, file = here::here("data", "glowbe_us6_pos.rda"))
rm(glowbe_us6_pos)
end_time <- Sys.time()
end_time - start_time
```



# Outro

```{r}
sessionInfo()
```


