---
title: "Vulgar language on the web across World Englishes - Part 1: data preparation"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: word_document
bibliography: bibliography.bib
link-citations: yes
---

# Intro

This document shows an analysis that was performed with the aim of finding differences in swearing across geographically distinct varieties of English around the world based on the GloWbe corpus. 

install packages

```{r install, eval = F, message=F, warning=F}
# install packages
install.packages("tidyverse")
install.packages("quanteda")
install.packages("here")
install.packages("udpipe")
install.packages("future")
install.packages("furrr")
install.packages("stringi")
install.packages("parallel")
install.packages("usethis")
```

load packages and set options

```{r act, message=FALSE, warning=FALSE}
# load packages
library(data.table)
library(tidyverse)
library(quanteda)
library(here)
library(stringi)
library(parallel)
library(usethis)
```

# Load data

define paths

```{r eval = F}
# list files
fls <- list.files("C:/Users/marti/OneDrive/Dokumente/UQ/Corpora/GloWbE", 
                  pattern = "txt", 
                  full.names = T, 
                  recursive = T, 
                  include.dirs = T)
# inspect
head(fls)
```

function for preparing data

```{r eval = F}
preptxt <- function(fls, var) {
  fln  <- fls[stringr::str_detect(fls, var)]
  txt <- sapply(fln, function(x){
    x <- scan(x, what = "char", quote = "", skipNul = T) %>%
      paste0(collapse = " ")  %>%
      stringr::str_replace_all("##", "~~~##") %>%
      stringr::str_split("~~~") %>%
      unlist() 
    }) %>%
    unlist()
  crp  <- names(txt)  %>% stringr::str_remove_all(".*GloWbE/") %>% stringr::str_remove_all("/Texts.*")
  sfl  <- names(txt)  %>% stringr::str_remove_all(".*/")
  fl  <- txt  %>% stringr::str_remove_all(" .*") %>% stringr::str_remove_all(".txt.*")
  df <- data.frame(crp, fl, sfl, txt)
  base::saveRDS(df, file = here::here("data", paste0(var, "df.rda", collapse = "", sep = "")))
}
```


```{r eval = F}
fls   <- fls[1:5]
```


# Processing

```{r eval = F}
# processing
preptxt(fls, var = "Australia") # Australia
preptxt(fls, var = "Bangladesh") # Bangladesh
preptxt(fls, var = "Canada") # Canada
preptxt(fls, var = "GB-Blog") # GB-Blog
preptxt(fls, var = "GB-General") # GB-General
preptxt(fls, var = "Ghana") # Ghana
preptxt(fls, var = "Hong Kong") # Hong Kong
preptxt(fls, var = "India") # India
preptxt(fls, var = "Ireland") # Ireland
preptxt(fls, var = "Jamaica") # Jamaica
preptxt(fls, var = "Kenya") # Kenya
preptxt(fls, var = "Malaysia") # Malaysia
preptxt(fls, var = "New Zealand") # New Zealand
preptxt(fls, var = "Nigeria") # Nigeria
preptxt(fls, var = "Pakistan") # Pakistan
preptxt(fls, var = "Philippines") # Philippines
preptxt(fls, var = "Singapore") # Singapore
preptxt(fls, var = "South Africa") # South Africa
preptxt(fls, var = "Sri Lanka") # Sri Lanka
preptxt(fls, var = "Tanzania") # Tanzania
preptxt(fls, var = "US-Blog") # US-Blog
preptxt(fls, var = "US-General") # US-General
```

check

```{r eval = F}
audf  <- base::readRDS(file = here::here("data", "Australiadf.rda"))
# inspect
head(audf); nrow(audf)
```

Clean text

write function to clean text

```{r eval = F}
cleantxt <- function(dfs){
  sapply(dfs, function(x) {
  nmfl <- stringr::str_remove_all(x, ".*/") %>% stringr::str_remove_all("df.rda")
  base::readRDS(file = x)  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt))  %>%
  base::saveRDS(df, file = here::here("data", paste0(nmfl, "dfc.rda", collapse = "", sep = "")))
}) }
```

apply function

```{r eval = F}
dfs <- list.files(here::here("data"), 
                  pattern = "df.rda", 
                  full.names = T, 
                  recursive = T, 
                  include.dirs = T)
# inspect
head(dfs)
```


```{r eval = F}
dfs <- dfs[1]
cleantxt(dfs)
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Australiadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Australiadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Bangladeshdf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Bangladeshdfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Canadadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Canadadfc.rda"))
```


```{r eval = F}
df <- base::readRDS(file = here::here("data", "GB-Blogdf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "GB-Blogdfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "GB-Generaldf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "GB-Generaldfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Ghanadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Ghanadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Hong Kongdf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Hong Kongdfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Indiadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Indiadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Irelanddf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Irelanddfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Jamaicadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Jamaicadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Kenyadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Kenyadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Malaysiadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Malaysiadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "New Zealanddf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "New Zealanddfc.rda"))
```


```{r eval = F}
df <- base::readRDS(file = here::here("data", "Nigeriadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Nigeriadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Pakistandf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Pakistandfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Philippinesdf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Philippinesdfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Singaporedf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Singaporedfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "South Africadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "South Africadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Sri Lankadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Sri Lankadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "Tanzaniadf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "Tanzaniadfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "US-Blogdf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "US-Blogdfc.rda"))
```

```{r eval = F}
df <- base::readRDS(file = here::here("data", "US-Generaldf.rda"))  %>%
  dplyr::mutate(ctxt = tolower(txt)) %>%
  dplyr::mutate(ctxt = iconv(ctxt, to = "ASCII"),
                ctxt = stringr::str_remove(ctxt, ".*? "),
                ctxt = stringr::str_remove_all(ctxt, "<.*?>"),
                ctxt = stringr::str_remove_all(ctxt, "[:punct:]"),
                ctxt = stringr::str_squish(ctxt)) 
# save
base::saveRDS(df, file = here::here("data", "US-Generaldfc.rda"))
```


# Regex

define regex lists

LDNOOBW (List-of-Dirty-Naughty-Obscene-and-Otherwise-Bad-Words)
See https://github.com/LDNOOBW/List-of-Dirty-Naughty-Obscene-and-Otherwise-Bad-Words/blob/master/en

```{r eval = F}
vulgar <- c("2g1c", "2 girls 1 cup", "acrotomophilia", "alabama hot pocket", "alaskan pipeline", "anal", "anilingus", "anus", "apeshit", "arsehole", "ass", "asshole", "assmunch", "auto erotic", "autoerotic", "babeland", "baby batter", "baby juice", "ball gag", "ball gravy", "ball kicking", "ball licking", "ball sack", "ball sucking", "bangbros", "bangbus", "bareback", "barely legal", "barenaked", "bastard", "bastardo", "bastinado", "bbw", "bdsm", "beaner", "beaners", "beaver cleaver", "beaver lips", "beastiality", "bestiality", "big black", "big breasts", "big knockers", "big tits", "bimbos", "birdlock", "bitch", "bitches", "black cock", "blonde action", "blonde on blonde action", "blowjob", "blow job", "blow your load", "blue waffle", "blumpkin", "bollocks", "bondage", "boner", "boob", "boobs", "booty call", "brown showers", "brunette action", "bukkake", "bulldyke", "bullet vibe", "bullshit", "bung hole", "bunghole", "busty", "butt", "buttcheeks", "butthole", "camel toe", "camgirl", "camslut", "camwhore", "carpet muncher", "carpetmuncher", "chocolate rosebuds", "cialis", "circlejerk", "cleveland steamer", "clit", "clitoris", "clover clamps", "clusterfuck", "cock", "cocks", "coprolagnia", "coprophilia", "cornhole", "coon", "coons", "creampie", "cum", "cumming", "cumshot", "cumshots", "cunnilingus", "cunt", "darkie", "date rape", "daterape", "deep throat", "deepthroat", "dendrophilia", "dick", "dildo", "dingleberry", "dingleberries", "dirty pillows", "dirty sanchez", "doggie style", "doggiestyle", "doggy style", "doggystyle", "dog style", "dolcett", "domination", "dominatrix", "dommes", "donkey punch", "double dong", "double penetration", "dp action", "dry hump", "dvda", "eat my ass", "ecchi", "ejaculation", "erotic", "erotism", "escort", "eunuch", "fag", "faggot", "fecal", "felch", "fellatio", "feltch", "female squirting", "femdom", "figging", "fingerbang", "fingering", "fisting", "foot fetish", "footjob", "frotting", "fuck", "fuck buttons", "fuckin", "fucking", "fucktards", "fudge packer", "fudgepacker", "futanari", "gangbang", "gang bang", "gay sex", "genitals", "giant cock", "girl on", "girl on top", "girls gone wild", "goatcx", "goatse", "god damn", "gokkun", "golden shower", "goodpoop", "goo girl", "goregasm", "grope", "group sex", "g-spot", "guro", "hand job", "handjob", "hard core", "hardcore", "hentai", "homoerotic", "honkey", "hooker", "horny", "hot carl", "hot chick", "how to kill", "how to murder", "huge fat", "humping", "incest", "intercourse", "jack off", "jail bait", "jailbait", "jelly donut", "jerk off", "jigaboo", "jiggaboo", "jiggerboo", "jizz", "juggs", "kike", "kinbaku", "kinkster", "kinky", "knobbing", "leather restraint", "leather straight jacket", "lemon party", "livesex", "lolita", "lovemaking", "make me come", "male squirting", "masturbate", "masturbating", "masturbation", "menage a trois", "milf", "missionary position", "mong", "motherfucker", "mound of venus", "mr hands", "muff diver", "muffdiving", "nambla", "nawashi", "negro", "neonazi", "nigga", "nigger", "nig nog", "nimphomania", "nipple", "nipples", "nsfw", "nsfw images", "nude", "nudity", "nutten", "nympho", "nymphomania", "octopussy", "omorashi", "one cup two girls", "one guy one jar", "orgasm", 
            "orgy", "paedophile", "paki", "panties", "panty", "pedobear", "pedophile", "pegging", "penis", "phone sex", "piece of shit", "pikey", "pissing", "piss pig", "pisspig", "playboy", "pleasure chest", "pole smoker", "ponyplay", "poof", "poon", "poontang", "punany", "poop chute", "poopchute", "porn", "porno", "pornography", "prince albert piercing", "pthc", "pubes", "pussy", "queaf", "queef", "quim", "raghead", "raging boner", "rape", "raping", "rapist", "rectum", "reverse cowgirl", "rimjob", "rimming", "rosy palm", "rosy palm and her 5 sisters", "rusty trombone", "sadism", "santorum", "scat", "schlong", "scissoring", "semen", "sex", "sexcam", "sexo", "sexy", "sexual", "sexually", "sexuality", "shaved beaver", "shaved pussy", "shemale", "shibari", "shit", "shitblimp", "shitty", "shota", "shrimping", "skeet", "slanteye", "slut", "s&m", "smut", "snatch", "snowballing", "sodomize", "sodomy", "spastic", "spic", "splooge", "splooge moose", "spooge", "spread legs", "spunk", "strap on", "strapon", "strappado", "strip club", "style doggy", "suck", "sucks", "suicide girls", "sultry women", "swastika", "swinger", "tainted love", "taste my", "tea bagging", "threesome", "throating", "thumbzilla", "tied up", "tight white", "tit", "tits", "titties", "titty", "tongue in a", "topless", "tosser", "towelhead", "tranny", "tribadism", "tub girl", "tubgirl", "tushy", "twat", "twink", "twinkie", "two girls one cup", "undressing", "upskirt", "urethra play", "urophilia", "vagina", "venus mound", "viagra", "vibrator", "violet wand", "vorarephilia", "voyeur", "voyeurweb", "voyuer", "vulva", "wank", "wetback", "wet dream", "white power", "whore", "worldsex", "wrapping men", "wrinkled starfish", "xx", "xxx", "yaoi", "yellow showers", "yiffy", "zoophilia")
```

manual list

```{r eval = F}
manuallist <- c("poofter", "lesbo", "fag", "fags", "faggot", "faggots", "fagend", "fage", "fagg", "fagot", "fagge", "fagots", "faget", "fagends", "faggs", "faghag", "dyke", "dike", "dykes", "dikes", "bugger",
                "buggers", "buggered", "buggering", "buggerall", "boffing", "bellend", "nympho", "nonce", "wanker", "wankers", "wank", "wanking", "wanka", "wanks", "wankie", "wanke", "wankan", "slag", "slagheap", "skank", "skanks", "shag", "shagging", "shaggin", "shagpile", "masterbate", "jerk", "circlejerk", "jerkoff", "jerks", "jerkoffs", "fuck", "fucking", "fucked", "eff", "fuckin", "effing", "fucks", "fk", "fac", "effie", "motherfucker", "fcuk", "clusterfuck", "mofo", "fuk", "effin", "fck", "motherfuckers", "fuckedup", "fucken", "effed", "fuckup", "phuc", "effi", "fke", "fcking", "fkn", 
                "fking", "fukien", "fks", "fak", "phukan", "fuckups", "fack", "phuck", "fukin", "fuckoff", "facc", "fuckyou", "effs", "fuckall", "fuking", "fka", "fukk", "fcks", "fkin", "f", "fucka", "mofos", "mindfuck", "fukang", "fuka", "fuckn", "fckn", "effies", "fuks", "fuke", "fki", "effyou", "effe", "phucking", "fukn", "fked", "fkd", "effedup", "headfuck", "fuked", "fuckton", "fucki", "fkz", "fckin", "fcked", "effen", "phucas", "muhfuck", "fuuuuuck", "fukkk", "fuki", "fuecks", "fuckiing", "effend", "friggin", "frigging", "friggen", "frigg", "friggs", "friggn", "feck", "fecking", "feckin", "fecked", "feek", "fecks", "fek", "bukkake", "bonk", "bonks", "bitch", "bitching", "bitches", "bitchin", "biatch", "bitchie", "bitchs", "bitchslap", "biatches", "btch", "bitchslapped", "bitchslapping", "bitchass", "shebitch", "richbitch", "bitchslaps", "bitchfights", "bitchfest", "whore", "whores", "hoa", "hoare", "hoar", "camwhore", "madonnawhore", "hoares", "ohora", "hoarfrost", "handhoe", "hoarelaval", "manwhore", "attentionwhore", "whoreism", 
                "whoreish", "whorehouse", "virginwhore", "mediawhore", "hoae", "crackwhore", "camerawhore", "slut", "sluts", "slutshamed", "slutz", "slutltagt", "huss", "hooker", "hookers", "ho", "hoe", "hor", "hore", "hos", "hoor", "hoedown", "hores", "hoing", "hoes", "hoas", "dildo", "boner", "boners", "bollocks", "bollix", "bollock", "twat", "twats", "tit", "tits", "titi", "titties", "titsup", "titis", "tities", "tites", "pussy", "octopussy", "pussyfooting", "pussyfoot", "pussyfooted", "pussybow", "pussys", "pussywhipped", "prick", "pricks", "pinus", "pinas", "panas", "penas", "pianus", "penus", "pecker", "muff", "minger", "knob", "knobs", "knobhead", "knobbing", "knobbed", "knobtwiddling", "knobbilled", "hobknob", "gash", "fanny", "fannys", "dick", "dicks", "dix", "dickhead", "dickheads", "dicke", "dicked", "dixs", "dickswinging", "dickss", "dickish", "cunt", "cnt", "cunts", "kuntz", "kunt", "cnts", "cock", "cocks", "cockup", "cockups", "cok", "cockahoop", "cockfighting", "cockeyed", "cockandbull", "cockadoodledoo", "cockcrow", "cocksucker", "cck", "weathercock", "cockblock", 
                "cockadoodledo", "cocksure", "cockfights", "cockadoodle", "cocksucking", "cocksuckers", "cockrock", "halfcock", "damn", "damned", "goddam", "goddamned", "goddamn", "damnd", "damnall", "dontgiveadamn", "paki", "pakis", "packie", "packy", "paky", "pakie", "nigger", "niggers", "nigga", "niggas", "niggaz", "nigge", "niggerlover", "japs", "jap", "darkie", "cracker", "coon", "coons", "chink", "chinks", "chinkchink", "libtards", "libtard", "tosser", "sissy", "sissys", "hag", "hags", "hagridden", "bint", "lmao", "lmfao", "lmfaos", "stuffedup", "spastic", "moron", "morons", "idiot", "idiots", "idiotproof", "idiotsavant", "idiotproofing", "git", "gits", "sonofabitch", "sonsofbitches", "bastard", "bastards", "basterds", "basterd", "bastardchild", "cornhole", "nutsack", "juggs", "butthole", "buttwipe", "bunghole", "boobs", "boob", "boobtube", "manboobs", "sideboob", "ballsack", "asshole", "assholes", "ahole", "aholes", "noasshole", "assholeish", "ass", "asses", "kickass", "badass", "smartass", "bigass", "asskicking", "asss", "halfass", "dumbass", "hardass", "asse", "crazyass", "painintheass", "assbackwards", "asskissing", "wiseass", "lameass", "asswipe", "fatass", "longass", "grownass", "assn", "whoopass", "asskicker", "weirdass", "wildass", "brokeass", "badasses", "smartasses", "jackass", "hugeass", "kissass", "cheapass", "asshat", "lazyass", "dumbasses", "punkass", 
                "asswhooping", "asslicking", "asshats", "asscovering", "weakass", "stupidass", "baddestass", "sillyass", "giantass", "fakeass", "coolass", "backwardass", "assbackward", "tightass", "suckass", "sexyass", "asswhipping", "asslickers", "asskickin", "asskickers", "assclowns", "arse", "arses", "arsehole", "arseholes", "smartarse", "arseend", "kickarse", "arsecovering", "paininthearse", "arsekicking", "arselicking", "shortarse", "arsekissing", "lardarse", "arsebackwards", "arseaboutface", "tightarse", "halfarse", "badarse", "shit", "bullshit", "shits", "bullshitting", "batshit", "shitton", "shitstorm", "nobullshit", "bullshits", "shithole", "shiteating", "shitt", "bullshite", "shitfaced", "shittalking", "horseshit", "shitkicking", "apeshit", "shitload", "pieceofshit", "chickenshit", "bullshitted", "shittin", "shitstirring", "shitscared", "shitstirrer", "shiti", "bullshitfree", "shitshow", "dogshit", "bullshiting", "shitreplacement", "shiting", "shitforbrains", "shitcovered", "jackshit", "batshitcrazy", "shittt", "shittonne", "shitloads", "shitkickers", "shithouse", "shithot", "shithead", "shitgt", "shitcanned", "bullshitt", "bshit", "piss", "pisspoor", "pissup", "pisstake", 
                "pisstaking", "pissant", "pissweak", "pissoff", "pisswarm", "pisstakes", "pissstained", "jism", "jiss", "cumming", "cummings", "crap", "craps", "crapper", "crapping", "crapped", "crappier", "crape", "crappie", "crapshoot", "crapness", "crappies", "crapp", "crapton", "crappers", "crapload", "crapi", "bullcrap", "crapps", "crapa", "bloody", "bloodyminded", "bloodymindedness", "bloodywell", "fanbloodytastic", "absobloodylutely", "pig", "pigs", "pigheaded", "pigtailed", "piglike", "pigignorant", "pigheadedness", "pigrearing", "pignosed", "pigignorance", "pigheadedly", "pigfaced", "pigugly", "pigsmashing", "pigshit", "pigfooted")
```

regex optimised

```{r}
regexlist <- c(# fuck
  "\\bf[uoaeck\\W]+\\b",
  "\\bf[uck\\W]+(er|ers|a|ing|er|a|az|erz|in)\\b",
  "\\bf[ock\\W]+(er|ers|a|ing|er|a|az|erz|in)\\b",
  "\\bf[eck\\W]+(er|ers|a|ing|er|a|az|erz|in)\\b",
  "\\bf[ack\\W]+(er|ers|a|ing|er|a|az|erz|in)\\b",
  "\\bf\\b",
  # Xfucker
  "\\b(mother|motha|cluster|head)f[auock\\W]+(er|ers|a|ing|er|a|az|erz|in)\\b",
  "\\bmofo[sz]*\\b",
  # phuk (phuc)
  "\\bphu[ck]+\\w*\\b",
  # eff
  "\\bef[f][ingedyoup]*\\b",
  # online
  "\\bwtf\\b", "\\basf\\b", "\\baf\\b", "\\blmao\\b", "\\bgtfo\\b", "\\bstfu\\b", "\\bfml\\b", "\\blmfao\\b", "\\bsmh\\b", "\\bbfd\\b", "\\bbfu\\b", "\\broflmao\\b",
  # arse
  "\\b[smrtighthalfbdck]*arse[holesz]*\\b",
  # ass
  "\\ba[sz]{2,}[esz]{0,2}]*\\b",
  # asshole
  "\\ba[sz]{2,}[(hole)]*[sz]{0,1}\\b",
  # bastard
  "\\bbastard\\w*\\b",
  # beaner 
  "\\bbeaner[s]*\\b",
  # bellend
  "\\bbellend[s]*\\b",
  # bloody
  "\\bblood[iyed]+\\b",
  # boobs
  "\\bboob[ies]*\\b",
  # butt
  "\\bbutt[swhipe]*\\b",
  # bitch
  "\\bb[i]*[a]*tch\\w*\\b",
  # bugger
  "\\bbugg[eringsal]+\\b",
  # cock
  "\\bco[ckx][szheaducker]*\\b",
  # chink
  "\\bch[i]*nk[s]*\\b",
  # coon
  "\\bcoon[s]*\\b",
  # crap
  "\\b[bull]*crap\\w*\\b",
  # cum
  "\\bcum[ming]*\\b",
  # cunt ("cunt", "cnt", "cunts", "kuntz", "kunt", "cnts")
  "\\b[ck]+[u]*nt[sz]*\\b",
  # damn
  "\\b[god]*damn\\b",
  # dick
  "\\bdi[xck]+[szinghead]*\\b",
  # dike
  "\\b[bul]*d[iy]*ke[sz]*\\b",
  # dildo
  "dildo[s]*",
  # boner
  "\\bboner[s]*\\b", 
  # bollocks
  "\\bboll[io]+[xcks]+\\b", 
  # darkie
  "\\bdarki[es]*\\b",
  # fag
  "\\bfag\\w*\\b",
  # feck
  "\\bfe[ck]+[enigsd]*\\b",
  # frig
  "\\bfrig[gineds]*\\b",
  # fanny
  "\\bfann[iesy]+\\b",
  # gash
  "\\bgash\\b",
  # gook
  "\\bg[o]*ok[s]*\\b",
  # idiot
  "\\bidiot\\w*\\b",
  # jackass
  "\\bjackass\\b",
  # jap 
  "\\bjap[s]*\\b",
  # jerk
  "\\bjerk[szinged]*\\b",
  # jiggerboo
  "\\b[j]+[i]+[g]+[ergbo]\\b",
  # jiss
  "\\bji[sszz]+\\b",
  # kike
  "\\bk[i]*ke[s]*\\b",
  # knob
  "\\bknob\\w*\\b",
  # lesbo"
  "\\blesbo[sz]*\\b",
  # minger  
  "\\bming[aers]+\\b",
  # moron
  "\\bm[ou]ron\\w*\\b",
  # muff
  "\\bmuff\\b",
  # nigger
  "\\bnigg[era]+\\w*\\b",
  # nonce
  "\\bnonce\\b",
  # nympho 
  "\\bnympho\\w*\\b",
  # paki
  "\\bpa[ck]+[yi]+[es]\\b",
  # pecker
  "\\bpe[ck]+er[s]*\\b",
  # pedo
  "\\bpedo[s]*\\b",
  # pikey
  "\\bpik[isey]+\\b",
  # pinus 
  "\\bp[iae]+n[ua]+s\\b",
  # piss
  "\\bpiss\\w*\\b",
  # pig
  "\\bpig[sz]*\\b",
  # poofter
  "\\bpooft\\w+\\b",
  # prick
  "\\bprick[s]*\\b",
  # pussy
  "\\bpuss[yies]+\\b",
  # poofter
  "\\bpoofter[sz]*\\b",
  # queef
  "\\bqu[ea]+f[szing]*\\b",
  # shag
  "\\bshag\\w*\\b",
  # shit
  "\\b[bull]*[s]+[h]+[i]+[t]+\\w\\b",
  # skank 
  "\\bskank[sz]*\\b",
  # slag 
  "\\bslag\\w*\\b",
  # slut
  "\\bslut\\w*\\b",
  # spastic
  "\\bspast\\w*\\b",
  # Xtard
  "\\b\\wtard[s]*\\b",
  # tits
  "\\btit[ties]\\b",
  # tranny
  "\\btr[a]*nn[yies]*\\b",
  # twat
  "\\btwat[s]*\\b",
  # wank
  "\\bwank[erings]*\\b",
  # whor[eish] 
  "\\b[w]*h[o]+r[eishng]*\\b",
  # whore 
  "\\bho[iae]+[szing]*\\b",
  # whore
  "\\b[camn]*whor\\w*\\b",
  # whore
  "\\bwhor\\w*\\b"
  )


```


```{r}

```


# Search

```{r}
# Australia
df <- base::readRDS(file = here::here("data", "Australiadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Australiares.rda"))
# inspect
head(res, 1000); table(res$keyword); nrow(res)
```

```{r}
# Bangladesh
df <- base::readRDS(file = here::here("data", "Bangladeshdfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Bangladeshres.rda"))
```

```{r}
# Canada
df <- base::readRDS(file = here::here("data", "Canadadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Canadares.rda"))
```

```{r}
# GB-Blog
df <- base::readRDS(file = here::here("data", "GB-Blogdfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Gbblogres.rda"))
```

```{r}
# GB-General
df <- base::readRDS(file = here::here("data", "GB-Generaldfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Gbgeneralres.rda"))
```

```{r}
# Ghana
df <- base::readRDS(file = here::here("data", "Ghanadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Ghanares.rda"))

# Hong Kong
df <- base::readRDS(file = here::here("data", "Hong Kongdfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Hongkongres.rda"))

# India
df <- base::readRDS(file = here::here("data", "Indiadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Indiares.rda"))

# Ireland
df <- base::readRDS(file = here::here("data", "Irelanddfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Irelandres.rda"))

# Jamaica
df <- base::readRDS(file = here::here("data", "Jamaicadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Jamaicares.rda"))

# Kenya
df <- base::readRDS(file = here::here("data", "Kenyadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Kenyares.rda"))

# Malaysia
df <- base::readRDS(file = here::here("data", "Malaysiadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Malaysiares.rda"))

# New Zealand
df <- base::readRDS(file = here::here("data", "New Zealanddfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Newzealandres.rda"))

# Nigeria
df <- base::readRDS(file = here::here("data", "Nigeriadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Nigeriares.rda"))

# Pakistan
df <- base::readRDS(file = here::here("data", "Pakistandfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Pakistanres.rda"))

# Philippines
df <- base::readRDS(file = here::here("data", "Philippinesdfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Philippinesres.rda"))

# Singapore
df <- base::readRDS(file = here::here("data", "Singaporedfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Singaporeres.rda"))

# South Africa
df <- base::readRDS(file = here::here("data", "South Africadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Southafricares.rda"))

# Sri Lanka
df <- base::readRDS(file = here::here("data", "Sri Lankadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Srilankares.rda"))

# Tanzania
df <- base::readRDS(file = here::here("data", "Tanzaniadfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Tanzaniares.rda"))

# US-Blog
df <- base::readRDS(file = here::here("data", "US-Blogdfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Usblogres.rda"))

# US-General
df <- base::readRDS(file = here::here("data", "US-Generaldfc.rda")) 
quanteda::kwic(quanteda::tokens(df$ctxt), regexlist, valuetype = "regex") %>%
  as.data.frame() -> res
# save
base::saveRDS(res, file = here::here("tables", "Usgeneralres.rda"))
```


# Outro

```{r}
sessionInfo()
```

# Appendix

testing

```{r, eval = F}
fln  <- fls[stringr::str_detect(fls, "Australia")]
txt <- sapply(fln, function(x){
    x <- scan(x, what = "char", quote = "", skipNul = T) %>%
      paste0(collapse = " ")  %>%
      stringr::str_replace_all("##", "~~~##") %>%
      stringr::str_split("~~~") %>%
      unlist()
    }) %>%
    unlist()
crp  <- fln  %>% stringr::str_remove_all(".*GloWbE/") %>% stringr::str_remove_all("/Texts.*")
sfl  <- fln  %>% stringr::str_remove_all(".*/")
fl  <- txt  %>% stringr::str_remove_all(" .*") %>% stringr::str_remove_all(".txt.*")
df <- data.frame(crp, fl, sfl, txt)
# save
base::saveRDS(df, file = here::here("data", paste0("Australia", "df.rda", collapse = "", sep = "")))
# inspect
str(df)
```
